---
title: "AR in Journalism"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(foreign)
library(stringr)
library(reshape)
library(phia)
library(ARTool)
library(dplyr)


# Functions
pairwise_test_levels = function(df, variable, levels, paired) {
  test_result = wilcox.test(df[df[, variable] == levels[1],]$value, 
                            df[df[, variable] == levels[2],]$value, 
                            paired=paired)
  return(test_result)
}

do_post_hoc_modalities = function(df) {
  modalities = list(c('AR', 'INTERACTIVE'), c('AR', 'STATIC'), 
                    c('INTERACTIVE', 'STATIC'))
  for (i in 1:length(modalities)) {
    pwm = pairwise_test_levels(df,'modality',modalities[[i]],FALSE)
    if (p.adjust(pwm$p.value) <= 0.05) {
      writeLines(paste0('Significant difference found between: ', modalities[[i]][1], 
                        ' and ', modalities[[i]][2], '\n--- Method=', 
                        pwm$method, '\n--- W=', pwm$statistic, '\n--- p-value=', pwm$p.value, '\n'))
    }
  }
}

do_post_hoc_pieces = function(df) {
  pieces = list(c('thai', 'syria'), c('thai', 'olympic'), 
                    c('syria', 'olympic'))
  for (i in 1:length(pieces)) {
    pwm = pairwise_test_levels(df,'piece',pieces[[i]],FALSE)
    if (p.adjust(pwm$p.value) <= 0.05) {
      writeLines(paste0('Significant difference found between: ', pieces[[i]][1], 
                        ' and ', pieces[[i]][2], '\n--- Method=', 
                        pwm$method, '\n--- W=', pwm$statistic, '\n--- p-value=', pwm$p.value, '\n'))
    }
  }
}

pairwise_test_modalities_piece = function(df, modalities, piece, paired) {
  test_result = wilcox.test(df[df$modality == modalities[1] & df$piece == piece,]$value, 
                            df[df$modality == modalities[2] & df$piece == piece,]$value, 
                            paired=paired)
  return(test_result)
}

do_post_hoc_modalities_pieces = function(df) {
  modalities = list(c('AR', 'INTERACTIVE'), c('AR', 'STATIC'), 
                    c('INTERACTIVE', 'STATIC'))
  pieces = c('thai', 'syria', 'olympic')
  for (i in 1:length(modalities)) {
    for (j in 1:length(pieces)) {
      pwm = pairwise_test_modalities_piece(df,modalities[[i]],pieces[j],FALSE)
      if (p.adjust(pwm$p.value) <= 0.05) {
        writeLines(paste0('Significant difference found between: ', modalities[[i]][1], 
                          ' and ', modalities[[i]][2], ' on piece ', pieces[j], '\n--- Method=', 
                          pwm$method, '\n--- W=', pwm$statistic, '\n--- p-value=', pwm$p.value, '\n'))
      }
    }
  }
}

prepare_data = function(df, cols) {
  # Select interested columns
  df = df[,cols]
  # Rename columns
  colnames(df) = c('subject','modality','olympic', 'syria', 'thai')
  # Remove NAs
  df = df[complete.cases(df), ]
  print(paste0('Subjects removed because of missing values: ', 79-nrow(df)))
  # Melting data
  m_df = melt(df, id=c('subject', 'modality'))
  colnames(m_df) = c('subject', 'modality', 'piece', 'value')
  m_df$modality = as.factor(m_df$modality)
  return (m_df)
}

do_analysis = function(df, cols) {
  # Define model
  m = art(value ~ piece * modality + (1|subject), data=df)
  # Conduct anova
  print(anova(m))
  # Analyze difference in interactions
  print(testInteractions(artlm(m, "piece:modality"), pairwise=c("piece", "modality"), 
                         adjustment="holm"))
}

# Load data
df = read.csv(file="./data/AR_ALL_DATA_ADDITIONS_LAST.csv", header=TRUE, sep=";")
u_df = read.csv(file="./data/usability.csv", header=TRUE, sep=",")
ra_df = read.csv(file="./data/relevancy_accuracy.csv", header=TRUE, sep=",")

# Drop some unused columns
drops = c("PRESENCE_TOTAL_OLYM","PRESENCE_TOTAL_SYRIA","PRESENCE_TOTAL_THAI")
ra_df = ra_df[ , !(names(ra_df) %in% drops)]

# Merge datasets
df = merge(df, u_df, by=c('SUBJECT', 'CONDITION'))
df = merge(df, ra_df, by=c('SUBJECT', 'CONDITION'))

# Inital data preparation
remove_comma = function(col) {
  return (as.numeric(gsub(',', '.', col)))
}
df_c = cbind(as.data.frame(apply(df[,c(1:4)], 2, as.factor)),
             as.data.frame(apply(df[,c(5:ncol(df))], 2, remove_comma)))
df_c[,2] = ifelse(df[,2]==1, 'AR', ifelse(df[,2]==2, 'INTERACTIVE', 'STATIC'))
```

Understanding the effect of Augmented Reality (AR) in Journalism. 

Three reading modalities were defined:

* Augmented Reality (AR)
* Interactive visualizations (INTERACTIVE)
* Static visualizations (STATIC)

Three pieces of information were defined:

* Chemical bomb attack in Syria (Syria)
* Youth soccer team reascue operation in Thailand (Thai)
* Olympici skate figure Nathan Chen (Olympic)

## Method

Align-and-rank data for non-paramentric ANOVA was applied to understand the 
effect of the reading modalities (see [here](http://depts.washington.edu/madlab/proj/art/index.html) 
for more information on the analysis method). The difference of difference method 
was employed to conduct post hoc pairwise comparison of levels within individual factors.

## Sense of Presence

Studying the effect of the modality and piece of information in the subjects'
sense of presence.

```{r}
i_cols = c('SUBJECT','CONDITION','PRESENCE_TOTAL_OLYM', 'PRESENCE_TOTAL_SYRIA', 
           'PRESENCE_TOTAL_THAI')
p_data = prepare_data(df_c, i_cols)
```

```{r sense_presence2, echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The sense of presence is significalty affected by the reading modality, the 
piece of information, and the interaction between them.*

### Post-Hoc on Modality

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities(p_data)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*The post hoc analysis shows that there is a significant difference in the sense
of presence between AR and Interactive and AR and Static on the syria and 
olympic pieces*

## Narrative Engagement and Transportation

Studying the effect of the modality and piece of information in the subjects'
narrative engagement and transportation.

```{r}
i_cols = c('SUBJECT','CONDITION','ENGAGE_TOTAL_OLYM', 'ENGAGE_TOTAL_SYRIA', 
           'ENGAGE_TOTAL_THAI')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The piece of information affects significantly the narrative engagement and
transportation. Additionally, the interaction between modality and piece of
information appears to signficanly influence engagement and transportation also.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*There is a significant difference in the engagement and transportation between 
AR and Interactive on the Olympic piece. A similar result is found between
Interactive and Static.*

## Perceived Learning

Studying the effect of the modality and piece of information in the subjects'
perceived learning.

```{r}
i_cols = c('SUBJECT','CONDITION', 'PERCEIV_LEARN_VISU_TOTAL_OLYM', 
           'PERCEIV_LEARN_VISU_TOTAL_SYRIA', 'PERCEIV_LEARN_VISU_TOTAL_THAI')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*What influence the perceived learning is the interaction between reading modality 
and piece of information.*

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*There is significant difference in the perceived learning between AR and Interactive
on the Thai piece.*

## Perceived Learning (II)

```{r}
i_cols = c('SUBJECT','CONDITION', 'PerceiveLearnGeneral_O', 
           'PerceiveLearnGeneral_T', 'PerceiveLearnGeneral_S')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

## Objective knowledge gain (I)

```{r}
i_cols = c('SUBJECT','CONDITION', 'OBJECT_LEARN_DESC_O', 
           'OBJECT_LEARN_DESC_ALL_S', 'OBJECT_LEARN_DESC_TOT_T')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
# column names different from paper
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The piece of information influences significantly the objective knowledge gain.
The interaction between modality and piece of information show to have a significant
effect as well.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*There is significant difference in the perceived learning between AR and Interactive
on the Syria piece.*

## Objective knowledge gain (II)

```{r}
i_cols = c('SUBJECT','CONDITION', 'OBJECT_LEARN_SPEC_ALL_O', 
           'OBJECTLEARN_SPEC_ALL_S', 'OBJECT_LEARN_SPEC_TOT_T')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
# column names different from paper
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The piece of information affects significantly the objective knowledge gain.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

## Perceived Realism and Authenticity

```{r}
i_cols = c('SUBJECT','CONDITION', 'JOURNAL_TOTAL_OLYM', 'JOURNAL_TOTAL_SYRIA', 
           'JOURNAL_TOTAL_THAI')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The piece of information affects significantly the perceived of realism and
authenticity.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

## Journalistic Norms

```{r}
i_cols = c('SUBJECT','CONDITION', 'AUTENTICITY_TOTAL_OLYM', 
           'AUTENTICITY_TOTAL_SYRIA', 'AUTENTICITY_TOTAL_THAI')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The pieces of information and their interactions with the reading modality 
influece significantly the journalism norms.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*There is a significant difference in the perceived learning between AR and Interactive
on the Thai piece. Similarly, the difference between Interactive and Static is
significant on the Thai piece.*

## Relevance

```{r}
i_cols = c('SUBJECT','CONDITION', 'Rel_O', 'Rel_S', 'Rel_T')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The pieces of information influece significantly in relevance.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*There is a significant difference in relevance between AR and Static
on the Thai piece.*

## Accuracy

```{r}
i_cols = c('SUBJECT','CONDITION', 'Acc_O', 'Acc_S', 'Acc_T')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The pieces of information influece significantly the accuracy.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

## Usability

```{r}
i_cols = c('SUBJECT','CONDITION', 'USABILITY_O', 'USABILITY_S', 'USABILITY_T')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
# columns name differente from paper
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

### Analysis of Variance

```{r}
# Define model
m = art(value ~ modality * piece + (1|subject), data=p_data)
anova(m)
```

*The pieces of information affect significantly the usability.*

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

## Intention to adopt the technology

```{r}
i_cols = c('SUBJECT','CONDITION', 'WILLING_TOTAL_OLYM', 'WILLING_TOTAL_SYRIA', 
           'WILLING_TOTAL_THAI')
p_data = prepare_data(df_c, i_cols)
```

```{r echo=FALSE}
with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                                response=value))
```

```{r}
# Define model
m = art(value ~ piece * modality + (1|subject), data=p_data)
anova(m)
```

## Engagement: Behavioral (Visuals)

```{r}
  i_cols = c('SUBJECT','CONDITION', 'SCREEN_TIME_VISUALS_O', 
             'SCREEN_TIME_VISUALS_S', 'SCREEN_TIME_VISUALS_T')
  p_data = prepare_data(df_c, i_cols)
```
 
```{r echo=FALSE}
  with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                               response=value))
```
 
### Analysis of Variance
 
```{r}
  m = art(value ~ piece * modality + (1|subject), data=p_data)
  anova(m)
```
 
### Post-Hoc on Modality

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities(p_data)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
``` 

*There is a significant difference in the users' behavior between AR and Interactive
on the pieces Thai and Olympic. Similarly, the difference between AR and Static is
significant on the Thai and Syria pieces.*

## Engagement: Behavioral (Text)
 
```{r}
  i_cols = c('SUBJECT','CONDITION', 'SCREEN_TIME_TEXT_O', 
             'SCREEN_TIME_TEXT_S', 'SCREEN_TIME_TEXT_T')
  p_data = prepare_data(df_c, i_cols)
```
 
```{r echo=FALSE}
  with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                               response=value))
```

### Analysis of Variance
 
```{r}
  m = art(value ~ piece * modality + (1|subject), data=p_data)
  anova(m)
```

### Post-Hoc on Modality

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities(p_data)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

*There is a significant difference in the users' behavior between AR and Static
on the Thai piece.*

## View again
 
```{r}
  i_cols = c('SUBJECT','CONDITION', 'Usabilit_Others_2_O', 
             'Usabilit_Sthers_2_S', 'Usabilit_Others_2_T')
  p_data = prepare_data(df_c, i_cols)
```
 
```{r echo=FALSE}
  with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                               response=value))
```

### Analysis of Variance
 
```{r}
  m = art(value ~ piece * modality + (1|subject), data=p_data)
  anova(m)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

## Interest
 
```{r}
  i_cols = c('SUBJECT','CONDITION', 'Usabilit_Others_1_O', 
             'Usabilit_Sthers_1_S', 'Usabilit_Others_1_T')
  p_data = prepare_data(df_c, i_cols)
```
 
```{r echo=FALSE}
  with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                               response=value))
```

### Analysis of Variance
 
```{r}
  m = art(value ~ piece * modality + (1|subject), data=p_data)
  anova(m)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

## Comfortable
 
```{r}
  i_cols = c('SUBJECT','CONDITION', 'Usabilit_Others_3_O', 
             'Usabilit_Sthers_3_S', 'Usabilit_Others_3_T')
  p_data = prepare_data(df_c, i_cols)
```
 
```{r echo=FALSE}
  with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                               response=value))
```

### Analysis of Variance
 
```{r}
  m = art(value ~ piece * modality + (1|subject), data=p_data)
  anova(m)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

### Post-Hoc on Interaction

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_modalities_pieces(p_data)
```

## Specific Learning Modified Analysis
 
```{r, warning=FALSE}
  i_cols = c('SUBJECT','CONDITION', 'OBJECT_LEARN_SPEC_ALL_O', 
             'OBJECTLEARN_TOTAL_S_ONLY4ITEMS', 'OBJECTLEARN_TOTAL_T_ONLY2ITEMS')
  
  p_data = prepare_data(filter(df_c, filter_. != 0), i_cols)
```
 
```{r echo=FALSE}
  with(p_data, interaction.plot(x.factor=piece, trace.factor=modality, 
                               response=value))
```

### Analysis of Variance
 
```{r}
  m = art(value ~ piece * modality + (1|subject), data=p_data)
  anova(m)
```

### Post-Hoc on Piece

```{r, warning=FALSE}
# Pairwise comparisons using Holm-Bonferroni correction
do_post_hoc_pieces(p_data)
```

## Summary

```{r, echo=FALSE, results='asis', warning=FALSE}
library(knitr)
s_res = data.frame(dependent_var=c('Sense of Presence', 'Narrative Engagement and Transportation',
                                   'Perceived Learning', 'Objective Knowledge Gain (I)',
                                   'Objective Knowledge Gain (II)', 'Perceived Realism and Authenticity',
                                   'Journalistic Norms', 'Usability (I)', 'Usability (II)',
                                   'Intention to adopt the technology', 
                                   'Engagement Behavioral (Visuals)',
                                   'Engagement Behavioral (Text)',
                                   'View again',
                                   'Inerest',
                                   'Comfortable',
                                   'Specific Learning'),
                   modality=c('*', ' ', ' ', ' ', ' ', ' ', ' ', '*', '*' ,' ', '*', '*', ' ', ' ', ' ', ' '),
                   piece=c('*', '*', ' ', '*', '*', '*', '*', '*', '*' ,' ', '*', '*', ' ', '*', '*', '*'),
                   inter_modality_piece=c('*', '*', '*', '*', ' ', ' ', '*', '*', '*', ' ', '*', '*', '*', ' ', '*', ' '))
kable(s_res, caption='Summary of significant difference between factors. * indicates significant difference')
```

There are significant differences on the sense of presence, users' behavior, and usability between modalities.
However, the interaction between modality and piece also affects significantly these factors.

```{r, echo=FALSE, results='asis', warning=FALSE}
s_res_inter = data.frame(dependent_var=c('Sense of Presence', 'Narrative Engagement and Transportation',
                                   'Perceived Learning', 'Objective Knowledge Gain (I)',
                                   'Journalistic Norms', 'Usability (I)', 'Usability (II)', 
                                   'Behavioral (I)', 'Behavioral (II)' , 'View Again', 'Comfortable'),
                         ar_inter_syria=c('*', ' ', ' ', '*', ' ', '*', ' ', ' ', ' ', ' ', ' '),
                         ar_inter_olympic=c('*', '*', ' ', ' ', ' ', ' ', ' ', '*', ' ', ' ', ' '),
                         ar_inter_thai=c(' ', ' ', '*', ' ', '*', '*', ' ', '*', ' ', ' ', '*'),
                         ar_static_syria=c('*', ' ', ' ', ' ', ' ', ' ', '*', '*', ' ', ' ', '*'),
                         ar_static_olympic=c('*', ' ', ' ', ' ', ' ', ' ', ' ', ' ', ' ', ' ', ' '),
                         ar_static_thai=c(' ', ' ', ' ', ' ', ' ', '*', '*', '*', '*', ' ', ' '),
                         inter_static_olympic=c(' ', '*', '*', ' ', ' ', ' ', ' ', '*', ' ', ' ', ' '),
                         inter_static_thai=c(' ', ' ', '*', ' ', '*', '*', '*', '*', ' ', ' ', '*'),
                         inter_static_syria=c(' ', ' ', '*', ' ', '*', '*', ' ', '*', '*', ' ', ' '))
kable(s_res_inter, 
      align=c('l', rep('c', 9)),
      caption='Summary of significant differences on pairwise comparison between modalities. * indicates significant difference')
```

There are a significant difference on the sense presence between AR and Interactive 
and AR and Static on the pieces Syria and Olympic. The difference in the narrative 
engagement and transportation is significant between AR and Interactive on the 
Olympic story. People reported a significant difference on the perceived learning 
between AR and Interactive on the Thai story. There are a significant difference
on the knowledge gain between AR and Interactive on the story about Syria. Journalism
norms are significantly different between AR and Interactive on the Thai story.
Depending on the story, Thai or Syria, there are a significant difference in 
usability between AR and Interactive and AR and Static.